### 2018-04-06 Cyber Security/Cyber Security.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{GCHQ Cyberfirst}
\rfoot{Page \thepage}

\usepackage{titlesec}

\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

\item Botnets - Malware that records the activities of the user

@@

\textbf{Signed programs} - The sue of cryptography when companies issue copies of a program, so that the user can check it for authenticity.

@@

The port decides how the data is handled when it reaches it's destination.\\

@@

When IP receives data from the internet, it removes the IO datagram and passes it to TCP.

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{GCHQ Cyberfirst}

%File specific Preamble
%Format Paragraphs correctly
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

@@

\item Botnets - A network of computers under the control of an attacker

@@

\textbf{Signed programs} - The use of cryptography when companies issue copies of a program, so that the user can check it for authenticity.

@@

The port decides how the data is handled when it reaches its destination.\\

@@

When IP receives data from the internet, it removes the IP datagram and passes it to TCP.

### 2018-04-06 Maths Notes/Further Pure/FP2/Polar Coordinates/Polar-Coordinates.tex
Update of all files to shorten preamble

\documentclass{article}
\usepackage{pgfplots}
\usepackage{tikz}
\usetikzlibrary{external}
\tikzexternalize[prefix=tikz/]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{titlesec}

\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\usepackage{cancel}

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}

>>>>

\documentclass{article}
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - FP2}

%File specific Preamble

%Externalise to save computation time
\usetikzlibrary{external}
\tikzexternalize[prefix=tikz/]

%Give paragraphs the same format as sections
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

### 2018-04-06 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{relsize}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - FP2}
\rfoot{Page \thepage}

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}

\usepackage{mathtools}

\newtagform{brackets}{[}{]}
\usetagform{brackets}

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - FP2}

%File specific Preable
\usepackage[super]{nth} %Provides 2nd etc

### 2018-04-06 Maths Notes/Statistics/S2/Exam Questions/CRVs/CRV Exam Questions.tex
S2 Notes Update
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{amssymb}

\pgfplotsset{width=10cm,compat=1.9}

\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Maths - S2}
\rfoot{Page \thepage}

@@

\subsection{Median}
To find the median set F(x) to 0.5. To do this you may need to convert the P.D.F to the C.D.F.\\
If the C.D.F has different equations for different ranges substitute in for any range. If the result is outside the range try a different range.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
    0, & \ x<0\\
    \frac{1}{4}x^2, &  0\leqslant x \leqslant 1\\
    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
    1 & x>2
  \end{array}\right.
$}\\
Testing between 0 and 1:
$$\frac{1}{4}x^2=0.5$$
$$x=1.41$$
As x is greater than 1 move to the next range
$$\frac{1}{20}x^4+\frac{1}{5}=0.5$$
$$x=1.57$$
This is in the range so is correct
\subsection{Mode}
With difficult problems differentiate f(x) and set to zero. Most will be able to be solved with logic though
\newpage
\section{Conversions between the P.D.F and C.D.F}
\subsection{P.D.F to C.D.F}
To convert the P.D.F to the C.D.F it must be integrated.\\
This integration is done as normal but needs no +C.\\
If there are multiple ranges add the maximum value of the previous range to find the C.D.F.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  f(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{1}{2}x, & \ 0\leqslant x\leqslant1\\
    \frac{1}{5}x^3, &  1\leqslant x \leqslant 2\\
    0 & \textrm{Otherwise}
  \end{array}\right.
$}\\
\\
Start by integrating the first range
$$\int_0^x \frac{1}{2}x \ dx=\frac{1}{4}x^2$$
Integrate the second range, remembering to add the area under the first range.
$$\int_1^x \frac{1}{5}x^3 dx+\int_0^1\frac{1}{2}x \ dx=\frac{1}{20}x^4+\frac{1}{5}$$
Write this in function form\\
\\
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
  0 & x<0\\
    \frac{1}{4}x^2, & \ 0\leqslant x\leqslant1\\
    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
    1 & x>2
  \end{array}\right.
$}\\
\subsection{C.D.F to P.D.F}
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
  0 & x<1\\
    \frac{4}{9}(x^2+2x-3), & \ 1\leqslant x\leqslant1.5\\
    1 & x>1.5\\
  \end{array}\right.
$}\\
\\
Differentiate $\frac{4}{9}(x^2+2x-3)$
$$\frac{8}{9}(x+1)$$
Write in function form\\
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{8}{9}(x+1), & \ 1\leqslant x\leqslant1.5\\
    0 & \textrm{Otherwise}\\
  \end{array}\right.
$}\\
\newpage
\section{Finding unknown constants}
To find unknown constants set one of the formulas to a value it is known to be and rearrange.\\
\\
For example with a C.D.F find the uppermost value and set it equal to one to find any constants.
\section{Finding probabilities}
For questions where a probability must be found, either an inequality or specific value, use the P.D.F or the C.D.F.
\subsection{Specific value}
To find the probability of a specific value substitute that value into the P.D.F.
\subsection{Inequality}
To find the probability of an inequality use the C.D.F. The C.D.F gives a less than or equal probability, so to find greater than probabilities the probability found must be subtracted from one.

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Maths - S2}

@@

\subsection{Median}
To find the median set F(x) to 0.5. To do this you may need to convert the P.D.F to the C.D.F.\\
If the C.D.F has different equations for different ranges substitute in for any range. If the result is outside the range try a different range.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
    0, & \ x<0\\
    \frac{1}{4}x^2, &  0\leqslant x \leqslant 1\\
    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
    1 & x>2
  \end{array}\right.
$}\\
Testing between 0 and 1:
$$\frac{1}{4}x^2=0.5$$
$$x=1.41$$
As x is greater than 1 move to the next range
$$\frac{1}{20}x^4+\frac{1}{5}=0.5$$
$$x=1.57$$
This is in the range so is correct
\subsection{Mode}
With difficult problems differentiate f(x) and set to zero. Most will be able to be solved with logic though
\newpage
\section{Conversions between the P.D.F and C.D.F}
\subsection{P.D.F to C.D.F}
To convert the P.D.F to the C.D.F it must be integrated.\\
This integration is done as normal but needs no +C.\\
If there are multiple ranges add the maximum value of the previous range to find the C.D.F.
\subsubsection{Example}
{\renewcommand{\arraystretch}{1.5}
$
  f(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{1}{2}x, & \ 0\leqslant x\leqslant1\\
    \frac{1}{5}x^3, &  1\leqslant x \leqslant 2\\
    0 & \textrm{Otherwise}
  \end{array}\right.
$}\\
\\
Start by integrating the first range
$$\int_0^x \frac{1}{2}x \ dx=\frac{1}{4}x^2$$
Integrate the second range, remembering to add the area under the first range.
$$\int_1^x \frac{1}{5}x^3 dx+\int_0^1\frac{1}{2}x \ dx=\frac{1}{20}x^4+\frac{1}{5}$$
Write this in function form\\
\\
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
  0 & x<0\\
    \frac{1}{4}x^2, & \ 0\leqslant x\leqslant1\\
    \frac{1}{20}x^4+\frac{1}{5}, &  1\leqslant x \leqslant 2\\
    1 & x>2
  \end{array}\right.
$}\\
\subsection{C.D.F to P.D.F}
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
  0 & x<2\\
    \frac{1}{20}(x^2-4), & \ 2\leqslant x\leqslant4\\
    \frac{1}{5}(2x-5), & \ 4< x\leqslant5\\
    1 & x>5\\
  \end{array}\right.
$}\\
\\
Differentiate $\frac{1}{20}(x^2-4)$
$$\frac{1}{10}x$$
Differentiate $\frac{1}{5}(2x-5)$
$$\frac{2}{5}$$
Write in function form\\
{\renewcommand{\arraystretch}{1.5}
$
  F(x)=\left\{
  \begin{array}{@{}ll@{}}
    \frac{1}{10}x, & \ 2\leqslant x\leqslant4\\
    \frac{2}{5}, & \ 4< x\leqslant5\\
    0 & \textrm{Otherwise}\\
  \end{array}\right.
$}\\
\newpage
\section{Finding unknown constants}
To find unknown constants set one of the formulas to a value it is known to be and rearrange.\\
\\
For example with a C.D.F find the uppermost value and set it equal to one to find any constants.
\section{Finding probabilities}
For questions where a probability must be found, either an inequality or specific value, use the P.D.F or the C.D.F.
\subsection{Specific value}
To find the probability of a specific value substitute that value into the P.D.F.
\subsection{Inequality}
To find the probability of an inequality use the C.D.F. The C.D.F gives a less than or equal probability, so to find greater than probabilities the probability found must be subtracted from one.

### 2018-04-06 Physics Notes/AS Level/Waves/Refraction, Diffraction and Interference/Refraction, Diffraction and Interference - AS.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{circuitikz}
\usetikzlibrary{decorations.pathmorphing,arrows,shapes,positioning,decorations.markings,angles,quotes}

\pgfplotsset{width=10cm,compat=1.9}
\usepackage{relsize}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}

\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{AS Level Physics - Waves}
\rfoot{Page \thepage}

\pgfkeys{/pgfplots/Axis Style/.style={
    width=13.5cm, height=10cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}
\pgfkeys{/pgfplots/Stationary Wave/.style={
    width=13.5cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=100,
    ymin=-1.2, ymax=1.2,
    xmin=0, xmax=13.0,
    domain=-4*pi:4*pi
}}

\tikzstyle arrowstyle=[scale=1]
\tikzstyle directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow[arrowstyle]{stealth}}}}]
\tikzstyle reverse directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrowreversed[arrowstyle]{stealth};}}}]

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{AS Level Physics - Waves}

%File specific Preamble
%Refraction settings
\usetikzlibrary{decorations.pathmorphing,arrows,shapes,positioning,decorations.markings,angles,quotes}
\tikzstyle arrowstyle=[scale=1]
\tikzstyle directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrow[arrowstyle]{stealth}}}}]
\tikzstyle reverse directed=[postaction={decorate,decoration={markings,
    mark=at position .65 with {\arrowreversed[arrowstyle]{stealth};}}}]

### 2018-04-06 Physics Notes/Fields and their consequences/Electromagnetic Induction/Electromagnetic Induction.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Fields}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}

\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\pgfkeys{/pgfplots/Axis Style 3/.style={
    width=7cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=200,
    ymin=-1.5, ymax=1.5,
    xmin=0, xmax=14.0,
    domain=-4*pi:4*pi
}}
\begin{document}
\begin{center}
\underline{\huge Electromagnetic Induction}
\end{center}
\section{Generating Electricity}
$ $\\
$ $\\

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Physics - Fields}

%File specific Preamble
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing,calc,quotes,angles}
\usepackage[super]{nth}
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\pgfkeys{/pgfplots/Axis Style 3/.style={
    width=7cm, height=5cm,
    axis x line=center, 
    axis y line=middle, 
    samples=200,
    ymin=-1.5, ymax=1.5,
    xmin=0, xmax=14.0,
    domain=-4*pi:4*pi
}}

\begin{document}
\begin{center}
\underline{\huge Electromagnetic Induction}
\end{center}
\section{Generating Electricity}
$ $\\
$ $\\

### 2018-04-06 Physics Notes/Further Mechanics and Thermal Physics/Thermal Physics/Thermal Physics.tex
Notes Update
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{tikz}
\usepackage{relsize}
\usetikzlibrary{scopes,quotes,arrows.meta,arrows,shapes.geometric}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage{gensymb}
\usepackage{tabularx}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\tikzstyle{arrow} = [thick,->,>=stealth]
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Further Mechanics and Thermal Physics}
\rfoot{Page \thepage}
\pgfdeclarelayer{background layer}
\pgfdeclarelayer{foreground layer}
\pgfsetlayers{background layer,main,foreground layer}

@@

\textcolor{red}{Replace M(Mass of all particles) with Nm(Number of particles $\times$ the mass of one particle}\\

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Physics - Further Mechanics and Thermal Physics}

%File specific Preamble
%Settings for cube diagram
\usetikzlibrary{scopes,quotes,arrows.meta,arrows,shapes.geometric}
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\textcolor{red}{Replace M(Mass of all particles) with Nm(Number of particles $\times$ the mass of one particle)}\\

### 2018-04-06 Physics Notes/Nuclear Physics/Radioactivity/Radioactivity.tex
Update of all files to shorten preamble

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{relsize}
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}
\usepackage[super]{nth}
\titlespacing\section{0pt}{14pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\newlength\tindent
\setlength{\tindent}{\parindent}
\setlength{\parindent}{0pt}
\renewcommand{\indent}{\hspace*{\tindent}}
\hyphenpenalty =10000
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Nuclear Physics}
\rfoot{Page \thepage}
\usepackage{mathtools}
\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]

\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{5pt plus 2pt minus 2pt}

>>>>

\documentclass{article}[18pt]
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Physics - Nuclear Physics}

%File specific preamble
%Diagrams
\usetikzlibrary{decorations, decorations.text,positioning,quotes,arrows.meta,decorations.markings,3d,shapes,decorations.pathmorphing}
\pgfplotsset{width=10cm,compat=1.9}

\usetikzlibrary{calc,quotes,angles}
\tikzstyle{arrow} = [thick,->,>=stealth]

%Proper paragraph formatting
\setcounter{secnumdepth}{4}
\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

### 2018-04-06 Physics Notes/Turning Points/Wave Particle Duality/Microscopes/Microscopes.tex
Update of all files to shorten preamble

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{blindtext}
\usepackage{textcomp}
\pagestyle{fancy}
\fancyhf{}
\rhead{Sam Robbins 13SE}
\lhead{A Level Physics - Turning Points}
\begin{document}
\begin{center}
\underline{\huge Microscopes}
\end{center}
\section{Producing electrons with de Broglie wavelength the size of an atom}
As shown in electron diffraction:
$$\lambda=\frac{h}{\sqrt{2meV}}$$
This can be rearranged to find the voltage required to produce electrons of a given wavelength. 
$$\lambda^2=\frac{h^2}{2meV}$$
$$V=\frac{h^2}{2me\lambda^2}$$
\section{Transmission electron microscope}
This involves firing a beam of electrons with anode voltage of 300kV at an ultra-thin specimen contained within the evacuated column of the microscope.\\
This beam of electrons if focused by a cylindrical magnetic condenser lens, which deflects electrons to form a wide beam that is incident on the spectrum.\\
\includegraphics[width=8cm]{tem.png}\\
When an electron wave encounters the specimen it can either:
\begin{itemize}
\item Pass straight through the specimen without interacting
\item Get absorbed
\item Diffract
\end{itemize}
The electrons that pass through the specimen form the main beam, and a series of additional magnetic lenses direct and focus this beam onto a fluorescent screen. This creates an image when the electrons strike a florescent screen. The darker areas of the image represent the parts of the specimen that are thicker as more electrons are absorbed.\\
\\
The image detail can be improved by increasing the anode voltage of the electron gun.\\
\\
The image detail may reduce when travelling through the specimen as some electrons may have a loss of speed, causing the magnetic lenses to be unable to focus the electrons, a type of material dispersion.
\section{Scanning tunnelling microscope}
The STM has a very fine conducting probe, which is used to scan a small area of the surface of a conducting sample. The probe is positioned so that the tip of the probe is 1nm above the surface of the sample. The STM creates images using an effect known as quantum tunnelling, which allows some of the electrons in the tip of the probe or the sample to move across the 1nm gap, creating a tunnelling current between the sample and the probe. A small voltage is maintained between the tip of the probe and the sample to ensure that the electrons cross the gap in only one direction, from negative to positive.\\
\includegraphics[width=5cm]{stm.png}\\
\\
Quantum tunnelling occurs because of the wave nature of electrons. Just as light can pass through a very thin metal film because the amplitude of the light is not reduced to zero by its passage through the film, matter waves can pass through an apparent barrier, such as an insulating air gap in a conducting circuit, if the gap is sufficiently narrow.\\
At room temperature the de Broglie wavelength of an electron in a metal is about 1nm, comparable to the gap between the sample surface and the probe tip, meaning there is a small probability that electrons can jump across the gap.\\
\\
A STM can be used in one of two ways:
\subsection{Method 1 - Constant height}
In this method the probe is kept at a constant height, so that only undulations in the surface of the sample affect the size of the gap. The smaller the gap, the more electrons move across the gap per second, increasing the current, which can then be measured.\\
The voltage between the surface and the probe tip must be kept constant, so the current at a given height is constant.\\
This has a vertical resolution of 0.001nm, much smaller than the smallest atom
\subsection{Method 2 - Constant current}
In this method the height of the probe is altered to keep the tunnelling current constant, and then variations in the vertical position of the probe can be used to image the surface of the sample.
\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{/home/sam/Documents/School_Notes/format}
\lhead{A Level Physics - Turning Points}

\begin{document}
\begin{center}
\underline{\huge Microscopes}
\end{center}
\section{Producing electrons with de Broglie wavelength the size of an atom}
As shown in electron diffraction:
$$\lambda=\frac{h}{\sqrt{2meV}}$$
This can be rearranged to find the voltage required to produce electrons of a given wavelength. 
$$\lambda^2=\frac{h^2}{2meV}$$
$$V=\frac{h^2}{2me\lambda^2}$$
\section{Transmission electron microscope}
This involves firing a beam of electrons with anode voltage of 300kV at an ultra-thin specimen contained within the evacuated column of the microscope.\\
This beam of electrons if focused by a cylindrical magnetic condenser lens, which deflects electrons to form a wide beam that is incident on the spectrum.\\
\includegraphics[width=8cm]{tem.png}\\
When an electron wave encounters the specimen it can either:
\begin{itemize}
\item Pass straight through the specimen without interacting
\item Get absorbed
\item Diffract
\end{itemize}
The electrons that pass through the specimen form the main beam, and a series of additional magnetic lenses direct and focus this beam onto a fluorescent screen. This creates an image when the electrons strike a florescent screen. The darker areas of the image represent the parts of the specimen that are thicker as more electrons are absorbed.\\
\\
The image detail can be improved by increasing the anode voltage of the electron gun.\\
\\
The image detail may reduce when travelling through the specimen as some electrons may have a loss of speed, causing the magnetic lenses to be unable to focus the electrons, a type of material dispersion.
\section{Scanning tunnelling microscope}
The STM has a very fine conducting probe, which is used to scan a small area of the surface of a conducting sample. The probe is positioned so that the tip of the probe is 1nm above the surface of the sample. The STM creates images using an effect known as quantum tunnelling, which allows some of the electrons in the tip of the probe or the sample to move across the 1nm gap, creating a tunnelling current between the sample and the probe. A small voltage is maintained between the tip of the probe and the sample to ensure that the electrons cross the gap in only one direction, from negative to positive.\\
\includegraphics[width=5cm]{stm.png}\\
\\
Quantum tunnelling occurs because of the wave nature of electrons. Just as light can pass through a very thin metal film because the amplitude of the light is not reduced to zero by its passage through the film, matter waves can pass through an apparent barrier, such as an insulating air gap in a conducting circuit, if the gap is sufficiently narrow.\\
At room temperature the de Broglie wavelength of an electron in a metal is about 1nm, comparable to the gap between the sample surface and the probe tip, meaning there is a small probability that electrons can jump across the gap.\\
\\
A STM can be used in one of two ways:
\subsection{Method 1 - Constant height}
In this method the probe is kept at a constant height, so that only undulations in the surface of the sample affect the size of the gap. The smaller the gap, the more electrons move across the gap per second, increasing the current, which can then be measured.\\
The voltage between the surface and the probe tip must be kept constant, so the current at a given height is constant.\\
This has a vertical resolution of 0.001nm, much smaller than the smallest atom
\subsection{Method 2 - Constant current}
In this method the height of the probe is altered to keep the tunnelling current constant, and then variations in the vertical position of the probe can be used to image the surface of the sample.
\end{document}
